YilunZhuCode

### 2024-04-16 Yilun Upload/YilunCode.Rmd
Update for MKtest and ADF test

```{r}
ts_Temperature_Monthly <- msts(Monthly_Data$Temperature, 
                           seasonal.periods =c(12),
                           start=c(2011,1)
                           )
#create a subset for training purpose
n_for = 24
ts_Temperature_Monthly_train <- subset(ts_Temperature_Monthly,
                                   end = length(ts_Temperature_Monthly)-n_for)

#create a subset for testing purpose
ts_Temperature_Monthly_test <- subset(ts_Temperature_Monthly,
                                   start = length(ts_Temperature_Monthly)-n_for)
```

>>>>

```{r}
ts_Temperature_Monthly <- msts(Monthly_Data$Temperature, 
                           seasonal.periods =c(12),
                           start=c(2011,1)
                           )
decomposed_Temperature <- decompose(ts_Temperature_Monthly, type = "additive")
plot(decomposed_Temperature)
#create a subset for training purpose
n_for = 24
ts_Temperature_Monthly_train <- subset(ts_Temperature_Monthly,
                                   end = length(ts_Temperature_Monthly)-n_for)

#create a subset for testing purpose
ts_Temperature_Monthly_test <- subset(ts_Temperature_Monthly,
                                   start = length(ts_Temperature_Monthly)-n_for)

MKTest <- MannKendall(ts_Temperature_Monthly)
print(summary(MKTest))

print(adf.test(ts_Temperature_Monthly, alternative = "stationary"))
